\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-15 latex/UMEM_CoSim.tex
Fixed the Quartier Nord analysis
I reassigned the CitySim outputs to Q(s) and the EnergyPlus outputs to
incorporate both zones.

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program
\citep{Yang:2012cr}.
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined previously \citep{thomas2014multiscale}. This effort is based on the utilization of the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

@@

\section{Implementation}\label{Implementation}
\subsection{Campus case study 1: EnergyPlus simulation vs. co-simulation}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. The campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces. The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.

>>>>

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. Much of the initial co-simulation work is at the subsystem and building-scales. Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}. At the building and urban-scale, EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}. 
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in a previous study \citep{thomas2014multiscale}. This study forms the basis for the methodology in the current effort. This process utilizes the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

@@

\section{Implementation}\label{Implementation}

\subsection{Campus case study 1: HPI Building}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. The campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces. The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.
